Constant Error Tolerance Computational Fuzzy Extractors

### 2014-02-07 constantRate/ConstCompFuzzExt.tex
Consistency of equality oracle notation

Let $\mathcal{O}$ be a $\ell$-composable VGB obfuscator with auxiliary input for point programs over $\zo^n$.  Let $W$ be a $(q, \alpha = \omega(\log n), \beta)$-unguessable block distribution.  Our goal is to show that for all $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} =\ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{sec}}(C|P)\geq |C|- \beta$. % for $\epsilon' = 2\epsilon_{obf} + (\ell - \beta)2^{-(\alpha-1)}$.
Suppose not, that is suppose there is some $s_{sec} = \poly(n)$ such that exists $\epsilon_{sec} = \poly(n)$ and $H^{\hill}_{\epsilon_{sec}, s_{sec}}(C|P) < |C|-\beta$.

By \defref{def:block guessable} there exists a set of indices $\mathcal{I}$ such that all blocks within $\mathcal{I}$ are unguessable.  Define by $C'$ the distribution of sampling a uniform codeword where all locations outside $\mathcal{I}$ are fixed.  Then $C | C_{\mathcal{I}^c} \overset{d}=C'$.  By \clref{cl:many locations ent}, we have that $\Hav(C|C_{\mathcal{I}^c} )= |C| -\beta$ and thus $\Hav(C'| C_{\mathcal{I}^c}) = |C| -\beta$.  
Let $D$ a distinguisher of size be some distinguisher of size at most $s_{sec}$ such that 
\[
| \expe[D(C, P)] - \expe[D(C', P)] > \epsilon_{sec} = 1/\poly(n).
\]  
Define the distribution $X$ as follows:
\[X_i =
\begin{cases}
W_i & C_i = 0\\
R_i & C_i = 1.
\end{cases}\]  By the security of obfuscation~(\defref{def:obf}), there exists a unbounded time simulator $S$~(making at most $q$ queries) such that
\begin{align}
\label{eq:dist before}
|\expe [D(P_1,..., P_\ell, C)] - \expe [S^{I_X(\cdot, \cdot)}(C)] |\leq \epsilon_{sec}/3.
\end{align}
We now prove $S$ cannot distinguish between $C$ and $C'$.
\begin{lemma}
\label{lem:sim cannot distinguish}
$\Delta(S^{I_X(\cdot, \cdot)}(C), S^{I_X(\cdot, \cdot)}(C')) \le (\ell-\beta) 2^{-(\alpha+1)}$.
\end{lemma}

\begin{proof}
\noindent It suffices to show that for any two codewords that agree on $\mathcal{I}^c$, the statistical distance is at most $(\ell-\beta)2^{-(\alpha+1)}$.
\begin{lemma}
\label{lem:codewords in I close}
Let $c^*$ be true value encoded in $X$ and let $c'$ a codeword in $C'$.  Then,
\[
\Delta( S^{I_X(\cdot, \cdot)}(c^*), S^{I_X(\cdot, \cdot)}(c')) \le ( \ell -\beta) 2^{-(\alpha+1)}.
\]
\end{lemma}
\begin{proof}
Recall that for all $i\in \mathcal{I}$, $\Hav(W_i | View(S))\geq \alpha$.  The only information about the correct value of $c_i^*$ is contained in the query responses.  When all responses are $0$ the view of $S$ is identical when presented with $c^*$ or $c'$.  We now show that for any value of $c^*$ all queries on $i \in \mathcal{I}$ return $0$ with probability $1-2^{-\alpha+1}$.  Suppose not, that is suppose, the probability of at least one nonzero response on index $i$ is $> 2^{-(\alpha+1)}$.  Since $w, w'$ are independent of $r_i$, the probability of this happening when $c^*_i = 1$ is at most $q/2^n$ or equivalently $2^{-n+\log q}$.  Thus, it must occur with probability:
\begin{align}
2^{-\alpha+1}&<\Pr[\text{non zero response location }i]\nonumber \\
 &= \Pr[c_i^* =1]\Pr[\text{non zero response location }i\wedge c_i^*=1]\nonumber \\&+ \Pr[c_i^*=0] \Pr[\text{non zero response location }i \wedge c_i^*=0]\nonumber \\
&\le 1\times 2^{-n+\log q} + 1\times  \Pr[\text{non zero response location }i \wedge c_i^*=0] \label{eq:ways to remove ent}
\end{align}
We now show that $n-\log q \geq \alpha$:
\begin{claim}
\label{cl:ent bounded away from n}
$\alpha \le n-\log q$
\end{claim}
\begin{proof}
It suffices to show that there exists a simulator $S$ making $q$ queries such that the remaining entropy in any block is at most $n-\log q$.  Let $W_i$ be a distribution, consider $S$ that asks the $q$ most likely outcomes, the total probability of this block must be at least $2^{-n+\log q}$.  After these queries the remaining min-entropy is at most:
\begin{align*}
\Hav(W_i | View(S)) &\leq  -\log \left(\Pr[\text{some }q_i=1]\times 1+ \Pr[\text{no }q_i=1]\times \Pr[\text{most likely outcome}|q_1,...,q_q]\right)\\
&\leq  -\log \left(\Pr[\text{some }q_i=1]\times 1\right)\\
&=-\log\left( 2^{-n+\log q} \right) = n-\log q
\end{align*}
This completes the proof of \clref{cl:ent bounded away from n}.
\end{proof}
\noindent
Rearranging terms in Equation~\ref{eq:ways to remove ent}, we have:
\begin{align*}
 \Pr[\text{non zero response location }i \wedge c_i=0] &>2^{-\alpha+1} - 2^{-(n-\log q)}=  2^{-\alpha}
 \end{align*}
 When there is a $1$ response and $c_i=0$ this means that there is no remaining min-entropy.  If this occurs with over $2^{-\alpha}$ probability this violates the block unguessability of $W$~(\defref{def:block guessable}).  By the union bound over the indices $i\in\mathcal{I}$ the total probability of a $1$ in $\mathcal{I}$ is at most $(\ell-\beta)2^{-\alpha+1}$. Recall that $c^*, c'$ match on all indices outside of $\mathcal{I}$. Thus, for all $c^*, c'$ the statistical distance is at most $(\ell- \beta)2^{-\alpha+1}$.  This concludes the proof of \lemref{lem:codewords in I close}
\end{proof}
By averaging over all points in $C'$ we conclude that $\Delta(S^{I_X(\cdot, \cdot)}(C), S^{I_X(\cdot, \cdot)}(C')) < (\ell -\beta)2^{-(\alpha+1)}$.  This completes the proof of \lemref{lem:sim cannot distinguish}.
\end{proof}

\noindent Now by the security of obfuscation we have that
\begin{align}
\label{eq:dist after}
|\expe [D(P_1,..., P_\ell, C') ]- \expe [S^{I_X(\cdot, \cdot)}(C')] |\leq \epsilon_{sec}/3.
\end{align}
Combining Equations~\ref{eq:dist before} and~\ref{eq:dist after} and \lemref{lem:sim cannot distinguish}, we have
\begin{align*}
\delta^{D}(( P, C), (P, C'))&\leq |\expe [D(P_1,..., P_\ell, C)] - \expe [S^{I_X(\cdot, \cdot)}(C)]| \\
&+|\expe[S^{I_X(\cdot, \cdot)}(C)] - \expe[S^{I_X(\cdot, \cdot)}(C')] |\\
&+|\expe [S^{I_X(\cdot, \cdot)}(C')] - \expe [D(P_1,..., P_\ell, C') ]|\\
&\leq \epsilon_{sec}/3+ (\ell-\beta)2^{-(\alpha-1)}+\epsilon_{sec}/3 \\
&\leq 2\epsilon_{sec}/3 + \ngl(n) < \epsilon_{sec}.
\end{align*}
This is a contradiction and completes the proof of \lemref{lem:security of cons}.
\end{proof}

>>>>

Let $\mathcal{O}$ be a $\ell$-composable VGB obfuscator with auxiliary input for point programs over $\mathcal{Z}$.  Let $W$ be a $(q, \alpha = \omega(\log n), \beta)$-unguessable block distribution.  Our goal is to show that for all $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} =\ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{sec}}(C|P)\geq |C|- \beta$. % for $\epsilon' = 2\epsilon_{obf} + (\ell - \beta)2^{-(\alpha-1)}$.
Suppose not, that is suppose there is some $s_{sec} = \poly(n)$ such that exists $\epsilon_{sec} = \poly(n)$ and $H^{\hill}_{\epsilon_{sec}, s_{sec}}(C|P) < |C|-\beta$.

By \defref{def:block guessable} there exists a set of indices $\mathcal{I}$ such that all blocks within $\mathcal{I}$ are unguessable.  Define by $C'$ the distribution of sampling a uniform codeword where all locations outside $\mathcal{I}$ are fixed.  Then $C | C_{\mathcal{I}^c} \overset{d}=C'$.  By \clref{cl:many locations ent}, we have that $\Hav(C|C_{\mathcal{I}^c} )= |C| -\beta$ and thus $\Hav(C'| C_{\mathcal{I}^c}) = |C| -\beta$.  
Let $D$ a distinguisher of size be some distinguisher of size at most $s_{sec}$ such that 
\[
| \expe[D(C, P)] - \expe[D(C', P)] > \epsilon_{sec} = 1/\poly(n).
\]  
Define the distribution $X$ as follows:
\[X_i =
\begin{cases}
W_i & C_i = 0\\
R_i & C_i = 1.
\end{cases}\]  By the security of obfuscation~(\defref{def:obf}), there exists a unbounded time simulator $S$~(making at most $q$ queries) such that
\begin{align}
\label{eq:dist before}
|\expe [D(P_1,..., P_\ell, C)] - \expe [S^{I_X(\cdot, \cdot)}(C, 1^{\ell \log |Z|})] |\leq \epsilon_{sec}/3.
\end{align}
We now prove $S$ cannot distinguish between $C$ and $C'$.
\begin{lemma}
\label{lem:sim cannot distinguish}
$\Delta(S^{I_X(\cdot, \cdot)}(C, 1^{\ell \log |Z|}), S^{I_X(\cdot, \cdot)}(C', 1^{\ell \log |Z|})) \le (\ell-\beta) 2^{-(\alpha+1)}$.
\end{lemma}

\begin{proof}
\noindent It suffices to show that for any two codewords that agree on $\mathcal{I}^c$, the statistical distance is at most $(\ell-\beta)2^{-(\alpha+1)}$.
\begin{lemma}
\label{lem:codewords in I close}
Let $c^*$ be true value encoded in $X$ and let $c'$ a codeword in $C'$.  Then,
\[
\Delta( S^{I_X(\cdot, \cdot)}(c^*, 1^{\ell \log |Z|}), S^{I_X(\cdot, \cdot)}(c', 1^{\ell \log |Z|})) \le ( \ell -\beta) 2^{-(\alpha+1)}.
\]
\end{lemma}
\begin{proof}
Recall that for all $i\in \mathcal{I}$, $\Hav(W_i | View(S))\geq \alpha$.  The only information about the correct value of $c_i^*$ is contained in the query responses.  When all responses are $0$ the view of $S$ is identical when presented with $c^*$ or $c'$.  We now show that for any value of $c^*$ all queries on $i \in \mathcal{I}$ return $0$ with probability $1-2^{-\alpha+1}$.  Suppose not, that is suppose, the probability of at least one nonzero response on index $i$ is $> 2^{-(\alpha+1)}$.  Since $w, w'$ are independent of $r_i$, the probability of this happening when $c^*_i = 1$ is at most $q/2^n$ or equivalently $2^{-n+\log q}$.  Thus, it must occur with probability:
\begin{align}
2^{-\alpha+1}&<\Pr[\text{non zero response location }i]\nonumber \\
 &= \Pr[c_i^* =1]\Pr[\text{non zero response location }i\wedge c_i^*=1]\nonumber \\&+ \Pr[c_i^*=0] \Pr[\text{non zero response location }i \wedge c_i^*=0]\nonumber \\
&\le 1\times 2^{-n+\log q} + 1\times  \Pr[\text{non zero response location }i \wedge c_i^*=0] \label{eq:ways to remove ent}
\end{align}
We now show that $n-\log q \geq \alpha$:
\begin{claim}
\label{cl:ent bounded away from n}
$\alpha \le n-\log q$
\end{claim}
\begin{proof}
It suffices to show that there exists a simulator $S$ making $q$ queries such that the remaining entropy in any block is at most $n-\log q$.  Let $W_i$ be a distribution, consider $S$ that asks the $q$ most likely outcomes, the total probability of this block must be at least $2^{-n+\log q}$.  After these queries the remaining min-entropy is at most:
\begin{align*}
\Hav(W_i | View(S)) &\leq  -\log \left(\Pr[\text{some }q_i=1]\times 1+ \Pr[\text{no }q_i=1]\times \Pr[\text{most likely outcome}|q_1,...,q_q]\right)\\
&\leq  -\log \left(\Pr[\text{some }q_i=1]\times 1\right)\\
&=-\log\left( 2^{-n+\log q} \right) = n-\log q
\end{align*}
This completes the proof of \clref{cl:ent bounded away from n}.
\end{proof}
\noindent
Rearranging terms in Equation~\ref{eq:ways to remove ent}, we have:
\begin{align*}
 \Pr[\text{non zero response location }i \wedge c_i=0] &>2^{-\alpha+1} - 2^{-(n-\log q)}=  2^{-\alpha}
 \end{align*}
 When there is a $1$ response and $c_i=0$ this means that there is no remaining min-entropy.  If this occurs with over $2^{-\alpha}$ probability this violates the block unguessability of $W$~(\defref{def:block guessable}).  By the union bound over the indices $i\in\mathcal{I}$ the total probability of a $1$ in $\mathcal{I}$ is at most $(\ell-\beta)2^{-\alpha+1}$. Recall that $c^*, c'$ match on all indices outside of $\mathcal{I}$. Thus, for all $c^*, c'$ the statistical distance is at most $(\ell- \beta)2^{-\alpha+1}$.  This concludes the proof of \lemref{lem:codewords in I close}
\end{proof}
By averaging over all points in $C'$ we conclude that $\Delta(S^{I_X(\cdot, \cdot)}(C, 1^{\ell \log |Z|}), S^{I_X(\cdot, \cdot)}(C', 1^{\ell \log |Z|})) < (\ell -\beta)2^{-(\alpha+1)}$.  This completes the proof of \lemref{lem:sim cannot distinguish}.
\end{proof}

\noindent Now by the security of obfuscation we have that
\begin{align}
\label{eq:dist after}
|\expe [D(P_1,..., P_\ell, C') ]- \expe [S^{I_X(\cdot, \cdot)}(C', 1^{\ell \log |Z|})] |\leq \epsilon_{sec}/3.
\end{align}
Combining Equations~\ref{eq:dist before} and~\ref{eq:dist after} and \lemref{lem:sim cannot distinguish}, we have
\begin{align*}
\delta^{D}(( P, C), (P, C'))&\leq |\expe [D(P_1,..., P_\ell, C)] - \expe [S^{I_X(\cdot, \cdot)}(C, 1^{\ell \log |Z|})]| \\
&+|\expe[S^{I_X(\cdot, \cdot)}(C, 1^{\ell \log |Z|})] - \expe[S^{I_X(\cdot, \cdot)}(C', 1^{\ell \log |Z|})] |\\
&+|\expe [S^{I_X(\cdot, \cdot)}(C', 1^{\ell \log |Z|})] - \expe [D(P_1,..., P_\ell, C') ]|\\
&\leq \epsilon_{sec}/3+ (\ell-\beta)2^{-(\alpha-1)}+\epsilon_{sec}/3 \\
&\leq 2\epsilon_{sec}/3 + \ngl(n) < \epsilon_{sec}.
\end{align*}
This is a contradiction and completes the proof of \lemref{lem:security of cons}.
\end{proof}
